A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-09 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.25cm]{images/3.png}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.25cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (i) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that its optical axis be made parallel with the scene plane's normal vector, (ii) rotating the $X$- and $Y$-axes to render them parallel with those of the virtual camera, and (iii) optionally translating along the normal direction to achieve the desired projected image dimensions.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}

>>>>

\begin{figure}
    \centering
    \subfloat[\centering Oblique view.]{{\includegraphics[height=4.2cm]{images/3.png}}}
    \qquad
    \subfloat[\centering Downwards view.]{{\includegraphics[height=4.2cm]{images/3_above3.png}}}
    \caption{The virtual camera is obtained by rotating the camera (top left, black) about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. The virtual projector is obtained by (i) rotating the projector (bottom left, black) about the point of intersection of its optical axis with the scene plane such that its optical axis be made parallel with the scene plane's normal vector, (ii) rotating the $X$- and $Y$-axes to render them parallel with those of the virtual camera, and (iii) optionally translating along the normal direction to achieve the desired projected image dimensions.} %The virtual projector is thus rendered fronto-parallel with the ground plane and axially aligned with the virtual camera.
    \label{fig:virtualproj}
\end{figure}
